\documentclass{sfuapproval}

\title{Algorithmic study of Kernel Contraction in $\mathcal{EL}$}
\thesistype{Thesis}
\author{Amr Dawood}
\previousdegrees{%
	B.Sc. (Hons.), German University in Cairo, 2011}
\degree{Master of Science}
\discipline{Computing Science}
\department{School of Computing Science}
\faculty{Faculty of Applied Sciences}
\copyrightyear{2017}
\semester{Fall 2017}
\date{September 13, 2017}

\keywords{Kernel Contraction; EL; Description Logic; Specificity; Localization}

\committee{%
	\chair{Fred Popowich}{Professor}
	\member{James P. Delgrande}{Senior Supervisor\\Professor}
	\member{David G. Mitchell}{Supervisor\\Associate Professor}
	\member{Kewen Wang}{External Examiner\\Professor}
}

%   PACKAGES AND CUSTOMIZATIONS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Add any packages or custom commands you need for your thesis here.
%   You don't need to call the following packages, which are already called in
%   the sfuthesis class file:
%
%   - appendix
%   - etoolbox
%   - fontenc
%   - geometry
%   - lmodern
%   - nowidow
%   - setspace
%   - tocloft
%
%   If you call one of the above packages (or one of their dependencies) with
%   options, you may get a "Option clash" LaTeX error. If you get this error,
%   you can fix it by removing your copy of \usepackage and passing the options
%   you need by adding
%
%       \PassOptionsToPackage{<options>}{<package>}
%
%   before \documentclass{sfuthesis}.
%

\usepackage{amsmath,amssymb,amsthm}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{algpseudocode}


\theoremstyle{plain}
\newtheorem{thm}{Theorem}[chapter]
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}



%   FRONTMATTER  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Title page, committee page, copyright declaration, abstract,
%   dedication, acknowledgements, table of contents, etc.
%

\begin{document}

\frontmatter
\maketitle{}
\makecommittee{}

\begin{abstract}
Kernel contraction is an interesting problem that can be considered a step towards belief revision. Kernels were introduced as a tool to determine why a given belief is accepted by the knowledge base. The aim of using kernels is to invalidate the reasons why that given belief is accepted, and hence rejecting it. We use Description Logic $\mathcal{EL}$ for two reasons: it is used in some large knowledge base applications, and it has a polynomial-time reasoning algorithm. In this study we introduce an algorithm that performs kernel contraction using network-flow problem. We evaluate the rationality of the algorithm by applying postulates that govern kernel contraction. We also explain two heuristics: localization and specificity, that can be used to arrive at more reasonable and common-sense solutions. We will also be focusing on the complexity of the algorithms as an indicator to their feasibility.
\end{abstract}


%\begin{dedication} % optional
%\end{dedication}
%
%
%\begin{acknowledgements} % optional
%\end{acknowledgements}

\addtoToC{Table of Contents}\tableofcontents\clearpage
%\addtoToC{List of Tables}\listoftables\clearpage
\addtoToC{List of Figures}\listoffigures





%   MAIN MATTER  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Start writing your thesis --- or start \include ing chapters --- here.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mainmatter%



\include{introduction}


\include{background}


\include{contraction}


\include{heuristics}


\include{conclusion}




%   BACK MATTER  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   References and appendices. Appendices come after the bibliography and
%   should be in the order that they are referred to in the text.
%
%   If you include figures, etc. in an appendix, be sure to use
%
%       \caption[]{...}
%
%   to make sure they are not listed in the List of Figures.
%

\backmatter%
	\addtoToC{Bibliography}
	\bibliographystyle{plain}
	\bibliography{references}

%\begin{appendices} % optional
%	\chapter{Code}
%\end{appendices}
\end{document}
